Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2019-02-13 papers/paper/paper.tex
Add capability to make the model/experimental stacked histogram plot for initial vs final displacement to make_all_stepping_plots.py.

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
  \caption{\textbf{Analysis of stepping independence.} Heatmap of MTBD displacement before and after a stepping cycle. Displacement defined as the unbinding MTBD's x coordinate minus the stationary MTBD's x coordinate, calculated before and after the step. Structure in the heat map suggests steps are not independent, but rather that correlation exists between starting position and step size.}
\label{fig:independence}
\end{figure}

>>>>

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}\\
  \includegraphics[width=\linewidth]{../../plots/stacked_displacement_histogram.pdf}
  \caption{\textbf{Analysis of stepping independence.} \textbf{a.)} Heatmap of MTBD displacement before and after a stepping cycle. Displacement defined as the unbinding MTBD's x coordinate minus the stationary MTBD's x coordinate, calculated before and after the step. Structure in the heat map suggests steps are not independent, but rather that correlation exists between starting position and step size. \textbf{b.)} Compound histogram of final displacement for different ranges of initial displacement.}
\label{fig:independence}
\end{figure}
